HaPy \\ Haskell for Python

### 2011-12-17 paper.tex

\section{Use}
% - Meshing python and haskell semantics

>>>>

\section{Use}
Importing a Haskell module into a Python program is easy with HaPy: simply add the line
\begin{minted}{python}
from HaPy import HsModule
\end{minted}
to the head of any Python script. This will dynamically load the specified Haskell module, so that any Haskell function defined in HsModule can be accessed and executed by the Python script. \\
Installing HaPy is similarly intuitive, but with the caveat that all libraries called by HaPy.hs must be dynamically-linkable. This means that all of the packages that HaPy.hs imports must be reinstalled with Cabal, using the \verb!--enable-shared! flag. \footnote{The requirement that these packages be dynamically-linkable is enforced by Python's ctypes module, which we use to marshall primitive types across the Haskell-Python interface.} \\
However, Haskell packages that are used by the user's Haskell code need not be dynamically-linkable. Indeed, on the Haskell side, no special support is needed by the user; literally any standard Haskell code will run with HaPy. All the issues of marshalling data and passing data to and from the Foreign Function Interface are managed by the code in HaPy.hs \\
This has the added benefit of enabling the user to call any code defined in the Haskell standard libraries from Python. 
% - Meshing python and haskell semantics
